Paper notes

### 2019-08-20 paper_notes.Rmd
OK, to finish and delete chunks

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Paper notes"
author: Rocco Paolillo
bibliography: "references.bib"
# target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
# csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
---

@@

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# library(kableExtra)
library(dplyr)
library(grid)
library(ggrepel)
library(magicfor)
library(dplyr)
library(plot3D)
library(rgl)
library(plotly)

@@

```{r heatmap-log,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}

@@

d_u_e <-  magic_result_as_vector()
d_u_v <- rep(seq(-1,1,by = 0.1),21) 
e_w <- 0
v_w <- 1-e_w
k <- 10

df <- data.frame(d_u_e,d_u_v,e_w,v_w)

title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))

 plot_fina_rast <-  suppressWarnings(suppressMessages(
    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
  ))

 fx <- d_u_e
 fy <- d_u_v
 fz <- ass$prap

 # persp(x = seq(-1, 1, by = 0.1),
   #   y = seq(-1, 1, by = 0.1),
   #   fz)

  d <- plot3d(fx,fy,fz,col="blue")
  rgl.postscript("d.eps",fmt="eps")

 test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) %>% layout(legend = list(x = 0.1, y = 0.9))
 #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
 #fx

# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)

# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")

#is.data.frame(ass)
#  print(plot_fina_rast)

print(plot_fina_rast)

@@

```{r heat2,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}

d_u_e <-  magic_result_as_vector()
d_u_v <- rep(seq(-1,1,by = 0.1),21) 
e_w <- 0
v_w <- 1-e_w
k <- 10

df <- data.frame(d_u_e,d_u_v,e_w,v_w)

title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))

 plot_fina_rast <-  suppressWarnings(suppressMessages(
    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
  ))

 fx <- d_u_e
 fy <- d_u_v
 fz <- ass$prap

 # persp(x = seq(-1, 1, by = 0.1),
   #   y = seq(-1, 1, by = 0.1),
   #   fz)

#  d <- plot3d(fx,fy,fz,col="blue")
#  rgl.postscript("d.eps",fmt="eps")

 test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
 #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
 #fx

# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)

# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")

#is.data.frame(ass)
#  print(plot_fina_rast)

print(test_trida)
print(plot_fina_rast)

@@

e_w <- 0.6
v_w <- 1 - e_w
k <- 10

@@

  print(final_prob)

>>>>

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Paper notes"
author: Rocco Paolillo
bibliography: "references.bib"
always_allow_html: yes
# target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
# csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
---

@@

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# library(kableExtra)
library(dplyr)
library(grid)
library(ggrepel)
library(magicfor)
# library(dplyr)
library(plot3D)
library(rgl)
library(plotly)
library(tidyr)
library(plyr)
library(rgl)
library(graphics)
library(cowplot)
library(magick)

@@

```{r heatmap-log,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=FALSE, echo=FALSE}

# # to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
# 
# magic_for(print,silent = TRUE)
# 
# for (i in seq (-1.0,1.0, by = 0.1)){
#   eth_diff <- rep(i,21)
#   print(eth_diff)
# }
# 
# d_u_e <-  magic_result_as_vector()
# d_u_v <- rep(seq(-1,1,by = 0.1),21) 
# e_w <- 0
# v_w <- 1-e_w
# k <- 10
# 
# df <- data.frame(d_u_e,d_u_v,e_w,v_w)
# 
# title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
# ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
# fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))
# 
#  plot_fina_rast <-  suppressWarnings(suppressMessages(
#     fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
#     + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
#   ))
#   
# 
#  fx <- d_u_e
#  fy <- d_u_v
#  fz <- ass$prap
#  
#  # persp(x = seq(-1, 1, by = 0.1),
#    #   y = seq(-1, 1, by = 0.1),
#    #   fz)
#  
#   d <- plot3d(fx,fy,fz,col="blue")
#   rgl.postscript("d.eps",fmt="eps")
#  
#  
#  test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) %>% layout(legend = list(x = 0.1, y = 0.9))
#  #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
#  #fx
#  
# # test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
#  
# # plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
#  
# #is.data.frame(ass)
# #  print(plot_fina_rast)
#  
# print(plot_fina_rast)
# 
# # knitr::include_graphics("gg.png" )

```{r heat2,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=FALSE, echo=FALSE}

# # to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
# 
# magic_for(print,silent = TRUE)
# 
# for (i in seq (-1.0,1.0, by = 0.1)){
#   eth_diff <- rep(i,21)
#   print(eth_diff)
# }
# 
# 
# d_u_e <-  magic_result_as_vector()
# d_u_v <- rep(seq(-1,1,by = 0.1),21)
# 
# k <- 10
# 
# e_w <- 0
# v_w <- 1-e_w
# df <- data.frame(d_u_e,d_u_v,e_w,v_w)
# 
# title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
# fin_prob <- mutate(df, proba = prob(d_u_e, d_u_v,e_w,v_w))
# fina_rast <- ggplot(fin_prob,aes(d_u_e,d_u_v))
# 
#  plot_fina_rast <-  suppressWarnings(suppressMessages(
#     fina_rast + geom_raster(aes(fill = proba)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
#     + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
#   ))
#   
# 
#  fx <- d_u_e
#  fy <- d_u_v
#  fz <- ass$prap
#  
#  # persp(x = seq(-1, 1, by = 0.1),
#    #   y = seq(-1, 1, by = 0.1),
#    #   fz)
#  
# #  d <- plot3d(fx,fy,fz,col="blue")
# #  rgl.postscript("d.eps",fmt="eps")
#  
#  
#  test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
#  #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
#  #fx
#  
# # test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
#  
# # plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
#  
# #is.data.frame(ass)
# #  print(plot_fina_rast)
# 
# print(test_trida)
# print(plot_fina_rast)
# 
# df

```{r testaa,  fig.width=12,fig.height=12,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}

@@

d_u_e <-  magic_result_as_vector()
d_u_v <- rep(seq(-1,1,by = 0.1),21)

k <- 10

#e_w <- 0
#v_w <- 1-e_w

prob_comb <- function(a){
title_cond_fin <- paste0("Ethnic weight = ",a$e_w*k,"; ","Value weight = ",a$v_w*k)
# fin_prob <- mutate(a, proba = prob(d_u_e, d_u_v,e_w,v_w))
fina_rast <- ggplot(a,aes(d_u_e,d_u_v))

 plot_fina_rast <-  suppressWarnings(suppressMessages(
    fina_rast + geom_raster(aes(fill = proba)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability",limits=c(0,1), breaks=seq(0,1,0.25))
  ))
 # print(plot_fina_rast)

 # fx <- d_u_e
# fy <- d_u_v
#  fz <- df_0$prob

# test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
}

df_0 <- mutate(data.frame(d_u_e,d_u_v,e_w=0,v_w=0), proba = prob(d_u_e, d_u_v,e_w,v_w))
df_05 <- mutate(data.frame(d_u_e,d_u_v,e_w=0.5,v_w=0.5),proba = prob(d_u_e, d_u_v,e_w,v_w))
df_maxe <- mutate(data.frame(d_u_e,d_u_v,e_w=1,v_w=0),proba = prob(d_u_e, d_u_v,e_w,v_w))
df_maxv <- mutate(data.frame(d_u_e,d_u_v,e_w=0,v_w=1),proba = prob(d_u_e, d_u_v,e_w,v_w))
df_r <- mutate(data.frame(d_u_e,d_u_v,e_w=0.1,v_w=0.1),proba = prob(d_u_e, d_u_v,e_w,v_w))
df_1 <- mutate(data.frame(d_u_e,d_u_v,e_w=10,v_w=10),proba = prob(d_u_e, d_u_v,e_w,v_w))

# df_05

plot_0 <- prob_comb(df_0)
plot_05 <- prob_comb(df_05)
plot_maxe <- prob_comb(df_maxe)
plot_maxv <- prob_comb(df_maxv)
plot_r <- prob_comb(df_r)
plot_1 <- prob_comb(df_1)

grid.arrange( plot_0,plot_05,plot_maxe,plot_maxv,plot_r,  plot_1,nrow=3,ncol=2)

@@

```{r test3D,  fig.width=18,fig.height=18,fig.cap="Probability to choose alternative location 3D",fig.align="center", include=TRUE, echo=FALSE}

 prob_3d <- function(b){
 fx <- d_u_e
  fy <- d_u_v
  fz <- b$prob

  tit <- paste0("Ethnic weight = ",b$e_w*k,"; ","Value weight = ",b$v_w*k, "\n\r -1:MIN Alternative, 1:MAX Alternative")

   test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", color=fz, mode="markers")  %>% 
    layout(
         #  title =  "Prob. relocate to alternative", font=list(size = 10),
     scene = list(
       xaxis = list(title = "x = Diff. Ethnic Ut."),
       yaxis = list(title = "y = Diff. Value Ut."),
       zaxis = list(title = "z = Probability")
     ), annotations = (list(x = 0.5, y = 0.8, text = tit ,
                           showarrow = F, font=list(size=18) #,
     #  xref='paper', yref='paper',
      # xanchor='right', yanchor='auto', xshift=0, yshift=0,
   #  font=list(size=15, color="red")
     ))
  # , legend = list(color = fz)
   ) %>% hide_colorbar()

 test_trida

# 
# 
#  plot3d_0 <- prob_3d(df_0)
#  plot3d_5 <- prob_3d(df_05)
#  plot3d_maxe <- prob_3d(df_maxe)
#  plot3d_maxv <- prob_3d(df_maxv)
#  plot3d_1 <- prob_3d(df_1)
#  plot3d_r <- prob_3d(df_r)

                  # prob_3d(df_0)
                  # prob_3d(df_05)
                  # prob_3d(df_maxe)
                  # prob_3d(df_maxv)
                  # prob_3d(df_1)
                  # prob_3d(df_r)
  # 
  # plot3d_0
  # plot3d_5
  # plot3d_maxe
  # plot3d_maxv
  # plot3d_1
  # plot3d_r

p_0 <- image_read("3d_0_0.png") %>% image_trim()
p_5 <- image_read("3d_5_5.png") %>% image_trim()
p_10_0 <- image_read("3d_10_0.png") %>% image_trim()
p_0_10 <- image_read("3d_0_10.png") %>% image_trim()
p_100 <- image_read("3d_100_100.png") %>% image_trim()
p_1 <- image_read("3d_1_1.png") %>% image_trim()

de <- ggdraw() + draw_image("3d_0_0.png")
fe <- ggdraw() + draw_image("3d_5_5.png")
te <- ggdraw() + draw_image("3d_10_0.png")
ne <- ggdraw() + draw_image("3d_0_10.png")
se <- ggdraw() + draw_image("3d_100_100.png")
ze <- ggdraw() + draw_image("3d_1_1.png")
# 
grid.arrange(de,fe,te,ne,se,ze,ncol=2,nrow=3)

# knitr::include_graphics("3d_0_0.png")
# knitr::include_graphics("3d_5_5.png")
# knitr::include_graphics("3d_10_0.png")
# knitr::include_graphics("3d_0_10.png")
# knitr::include_graphics("3d_100_100.png")
# knitr::include_graphics("3d_1_1.png")

@@

e_w <- 100
v_w <- 100
k <- 10

@@

  plot(final_prob)
